DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-18 paper/evaluation-cachepart.tex
remove fixme. replace track 1 picture.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/palloc_multicore}
  \caption{Cache space sensitivity of the DNN controller. \fixme{I
      think 'no part.' bar is not necessary here.}}
  \label{fig:palloc_multicore}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/palloc_bandwidth_exectime}
  \caption{Average processing time vs. the number of memory
memory intensive co-runners. Unlike
Figure~\ref{fig:perf_vs_bandwidth}, the shared L2 cache is equally
partitioned and each task is given a dedicated cache
partition. \fixme{how about changing the figure style to be the same
  as Figure 9.}}
  \label{fig:palloc_bandwidth_exectime}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/palloc_multicore}
  \caption{Cache space sensitivity of the DNN controller.}
  \label{fig:palloc_multicore}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/palloc_bandwidth_exectime}
  \caption{Average processing time vs. the number of memory
memory intensive co-runners; Each core (task) is given a equal-sized
dedicated cache partition.}
  \label{fig:palloc_bandwidth_exectime}
\end{figure}
